{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-07-02 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
??
Friday

\begin{abstract}
Urban regions are discrete urban areas with various socio-economic relationships and citizen commute patterns.
Defining the boundaries of urban regions is important to a variety of urban planning applications.
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter regional activities.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas that provides a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national (Great Britain) and municipal scale (the London metropolis).
While our results corresponded well to the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
\newline

@@

\section{Introduction}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity across the borders.
Urban boundaries that respect the human interaction space can be very important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is modeled as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\citep{ratti2010}.
Extending the previous method to different countries~\citep{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\citep{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

@@

In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions.
Specifically, the spatial interactions refer to the actual movements of Twitter users (i.e., the reallocation across the geographical space), which were extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the country level)~\citep{hawelka,jurdak2015}.
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}. 
We argue here that by investigating Twitter user mobility patterns, it provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.

We delineated the geography of urban boundaries in Great Britain by imposing a virtual fishnet over the islands of Great Britain.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\citep{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\citep{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges starting from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of the urban space in Great Britain.
As the depicted urban boundaries exhibit a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas. 
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
It provides a new understanding of the interactions between human activity and urban structures.

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them.
For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
\cite{
However, the spatial extent of these defined units overlaps via connections of various human activities amongst themselves, such as social-economic relations and commute patterns of citizens, where certain groups of units are more strongly connected as clusters than others.

how citizens perceive, organize their image of a city and interact with the urban environments. On the other hand, today’s urban boundaries (i.e. edges and districts) are usually defined by government agencies for political and administrative purposes. A fundamental question for this “top-down” based approach to defining urban boundaries is whether it reflects the real situations of humans interacting across space, such as commuting or trading between the borders. Further, the urban boundaries that respect how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.

The spatial extent of those places

@@

>>>>

\begin{abstract}
Existing urban boundaries are usually defined by government political and administrative purposes, however, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
Defining urban boundaries with considerations of socio-economic relationships and citizen commute patterns is important for many aspects in urban planning.
In this study, we presented a method to redraw urban boundaries based upon human interaction with the physical space.
Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national (Great Britain) and municipal scales (the London metropolis).
While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
\newline

@@

\section{Introduction}
Official urban boundaries are defined by government agencies for political and administrative purposes.
Urban environments are conceptualized as spaces that are recreated and formed by human activities~\citep{schliephake}.
A fundamental question when using the administrative, ``top-down'', approach to defining urban boundaries is whether the outcome reflects the spatial interactions of humans.
These interactions can take the form of trade, commerce, social connections, and political activity across borders.
Urban boundaries that respect the human interaction space are important to city planning, traffic management and resource allocation~\citep{gao2014, jiang2015,liu2015,long2015}.
Many studies adopt a ``bottom-up'' approach to urban boundary delineation, where the geographic space is partitioned into small units and each unit is represented as a node within a network structure.
A suitable community detection algorithm is applied to partition the network and associated geographic space based on the strength of human interaction among the nodes~\citep{lancichinetti2009}.
Different social and physical human interactions were considered to establish the edges of the network connecting the nodes.
For example, a large set of telephone call records were used to represent the network of human interaction across space to delineate urban boundaries in Great Britain~\citep{ratti2010}.
Extending the previous method to different countries~\citep{sobolevsky2013}, the authors argue that this method yields cohesive geographic divisions that follow the socio-economic boundaries.
While other researchers use social ties of Twitter users to identify cohesive regions for different countries across the world~\citep{kallus2015}, they found evidence for dividing the urban space due to local conflicts and cross-country unifying trends that further support the ``bottom-up" approach to mapping non-administrative anthropographic boundaries.

@@

In this study, we describe a novel approach to delineating urban boundaries from a mobility network of physical human spatial interactions.
Specifically, the spatial interactions refer to the actual movements of Twitter users (i.e., the reallocation across the geographical space), which were extracted from more than 69 million Twitter messages from June $1^{st}$ to December $31^{st}$, 2014.
Geo-located Twitter data is proven to be a useful source for studying human mobility patterns at large spatial scales (e.g. the national level)~\citep{hawelka,jurdak2015}.
In addition, Twitter data are not as sensitive to user privacy issues and do not exhibit spatial granularity that is limited to the postal code level~\citep{thiemann}. 
We argue here that by investigating Twitter user mobility patterns, we can provide a different view of non-administrative units based on physical commutes rather than social ties or phone call initiation. 
A unique advantage is that non-administrative anthropographic urban boundaries can be delineated in a hierarchical fashion based upon different ranges of physical movement, which are inferred from the collective mobility patterns of Twitter users in Great Britain.

We delineated the geography of urban boundaries in Great Britain by imposing a virtual fishnet over the islands of Great Britain.
Twitter user movements were used to establish the connections between the fishnet's cells to form a connectivity network, where each cell acts as a node within the network.
We applied the map equation algorithm~\citep{domenico2015} to partition the network and associate geographic regions.
The map equation algorithm was selected to avoid the inherent resolution problem~\citep{fortunato2007} of the common modularity maximization method~\citep{newman2006}. 
We found that the collective mobility patterns of Twitter users in Great Britain are divided into several distance ranges ranging from short, intra- to inter-city movements with clear distinction points. 
The identification of connected regions at each of these distance ranges yielded hierarchical boundaries of urban spaces in Great Britain.
As the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
The well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas. 
Our study provides a first step in connecting human mobility research with the definition of non-administrative anthropographic urban boundaries based on Twitter user spatial interaction. 
This provides a new understanding of the interactions between human activity and urban structures.

\section{Background and Related Work}
In real-world geography, urban regions are discrete individuals, with or without physical boundaries separating them~\citep{jiang2015}.
For political and administrative purposes, government agencies define various sets of boundaries to partition the geographical space into units at different spatial scale, for instances, states, counties or census tracts and electoral districts.
However, the spatial extents of these defined units often overlap and agglomerate depending how citizens perceive, organize their image of a city and interact with the urban environments~\citep{lynch1960}.
Connections are made among these units with various human activities crossing the boarders, such as social-economic relations and commute patterns of citizens. 
In such cases, certain groups of units are more strongly connected as clusters than others, and the boarders of agglomeration of these units

how people naturally interact with the space can be in grate importance for decision makers regarding city planning, resource allocation and even marketing campaigns.

@@

\bibitem[\protect\citeauthoryear{Lynch}{1960}]{lynch1960}
Lynch, K., 1960. The image of the city. MIT press.
